\documentclass[12pt]{report}

% Packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{fancyhdr}

% Page Setup
\geometry{a4paper, margin=1in}
\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

% Title Page
\title{Deep Learning Project Report}
\author{Daniel Mașniță\\ \\ Theodor Ionică}
\date{}



% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Deep Learning Project Report}
\fancyhead[R]{\leftmark}
\fancyfoot[C]{\thepage}

\begin{document}

%% Title Page
\maketitle
%\vfill
%\begin{flushright}
%    \textbf{Your Name} \\
%\end{flushright}
%\newpage

% Table of Contents
\tableofcontents
\newpage

% Introduction
\chapter{Introduction}
\label{chap:introduction}
I fuck you in the mouth motherfucker

BIIIIIITCH!

% Related Work
\chapter{Related Work}
\label{chap:related_work}
This chapter reviews the existing literature and related work in the field of deep learning relevant to the project.

% Data
\chapter{Data}
\label{chap:data}
This chapter describes the dataset(s) used in the project, including how they were collected, preprocessed, and any relevant statistics or visualizations.

% Methodology
\chapter{Methodology}
\label{chap:methodology}
This chapter details the methods and techniques used in the project, including model architectures, training procedures, and any specific algorithms or tools utilized.

% Results and Discussion
\chapter{Results and Discussion}
\label{chap:results_discussion}
This chapter presents the results of the project, including performance metrics, comparisons with baselines, and interpretations of the findings. It also discusses any challenges encountered and how they were addressed.

% Conclusion
\chapter{Conclusion}
\label{chap:conclusion}
This chapter summarizes the project's findings, discusses their implications, and suggests potential future work.

% Bibliography
\begin{thebibliography}{99}
\bibitem{example1} Author, A. (Year). Title of the paper. \textit{Journal Name}, \textit{Volume}(Issue), pages.
\bibitem{example2} Author, B. (Year). Title of the book. Publisher.
\end{thebibliography}

\end{document}
